\documentclass[10pt]{article}
\usepackage{cv} %use xelatex
\title{Curriculum Vitae}
\author{Andrew J.\ Zimolzak}
\begin{document}

\thispagestyle{fancy}

\section*{Personal Information}

\begin{tabular}{l l}
\textbf{Research address:}  & \textbf{Home address:}\\
x-office    & x-home\\
x-ocity    & x-hcity\\
x-phone    & x-mobile\\
zimolzak@bcm.edu\\
\\
\textbf{Birth date:} x-bday\\
\textbf{Birthplace:} x-bplace
\end{tabular}




\section*{Education}

\textbf{Michigan State University.} 8/13/1998\ndash5/3/2002.\\
150 Administration Building; East Lansing, MI 48824-0210.\\
BS in Biochemistry with High Honor. Member of the Honors College.

\textbf{Washington University in St.\ Louis School of Medicine.}
8/19/2002\ndash\linebreak[0]5/6/\linebreak[0]2007.\\
Campus Box 8021, 660 S.\ Euclid; St.\ Louis, MO 63110.\\
MD.

\textbf{University of Missouri-Columbia.} 7/1/2007\ndash6/30/2008.\\
MA419 Medical Sciences Building DC043.00; Columbia, MO 65212.\\
Internal medicine PGY 1.

\textbf{Saint Louis University Hospital.} 7/1/2008\ndash6/30/2010.\\
3635 Vista Avenue, 14th Floor S, Desloge Towers; St.\ Louis MO
63110-0250.\\
Internal medicine PGY 2 and 3.

\textbf{Harvard Medical School.} 7/1/2011\ndash5/30/2013.\\
25 Shattuck Street; Boston, MA 02115.\\
MMSc in Medical Informatics.




\section*{Professional Experience} % reverse chron

\textbf{Clinical informatician} at the VA Center for Innovations in
Quality, Effectiveness and Safety (IQuESt), and at the Baylor
Institute for Clinical and Translational Research,
11/12/2018\ndash{}present. \textbf{Assistant professor,} Baylor
College of Medicine. I am a practicing physician with with significant
personal experience writing reusable \textbf{database, statistical,
  and machine learning} computer code for research. I unify large
collections of fragmented data elements to into clinically meaningful
concepts, thus making diverse clinical research studies possible. This
work is known by several names: \emph{secondary use} of electronic
health record data, \emph{clinical research informatics,} or
\emph{phenotyping.} I interpret clinical language and systems for data
pull engineers/analysts, or vice versa (interpreting technical
language for clinical investigators). I access a data warehouse
covering $> 20$ million unique individuals, and billions of
observations, from 1999 to the present, aggregated from 130 VA sites
(but incompletely standardized/harmonized). Major projects include
disseminating algorithms to detect missed laboratory test follow-ups,
and clinical trials matching. I also work as a \textbf{teaching
  attending} on the VA hospitalist service, supervising house staff
and students. Supervisors: Hardeep Singh, Chris Amos, Andrew Caruso,
Lindsey Gay.

\textbf{Clinical informatician,} Massachusetts Veterans Epidemiology
Research and Information Center (MAVERIC),
10/20/\linebreak[0]2014\ndash{}11/9/2018. \textbf{Assistant
  professor,} Boston University School of Medicine,
8/2016\ndash{}11/2018, and reciprocal appointment as Lecturer, Harvard
Medical School. My work enabled a \textbf{genomic precision medicine}
platform and learning health system for cancer, as well as a
13,000-subject point of care, randomized \textbf{comparative
  effectiveness trial} of two antihypertensives. Developed (2016) a
system to ensure \textbf{reusable phenotyping algorithms} for genomic
association and other studies, still in use as of 2024. Personally
exported and encrypted data from this system to the mirror system at
Oak Ridge National Laboratory (2018). Served as \textbf{co-program-director} of
the Big Data-Scientist Training Enhancement Program (BD-STEP) site in
Boston, and as principal investigator on a study of genomic predictors
of stage of lung cancer at presentation. Mentored an internal
medicine resident, who helped me make a highly accurate
\textbf{natural language processing classifier} of serum protein
electrophoresis reports. Inpatient medicine \textbf{teaching
  attending} at the VA hospital. Supervisors (research): Nhan Do,
Valmeek Kudesia, Mary Brophy, Louis Fiore. Clinical: Steven Simon, Jay
Orlander, Anthony Breu.

\textbf{Research collaborator,} Massachusetts Institute of Technology,
Laboratory for Computational Physiology,
12/6/2013\ndash{}\linebreak[0]9/2016. Lead clinician on a project to
develop a data-based definition of acute kidney injury, using records
of 11,000 patients from MIMIC II, an open collection of intensive care
unit data covering 8 years. Collaborated on writing and submitting a
R25 grant. Professor: Leo Celi.

\textbf{Research fellow,} Children's Hospital Informatics Program,
Intelligent Health Lab\-o\-ra\-to\-ry,
\linebreak[0]7/1/\linebreak[0]2011\ndash{}\linebreak[0]1/31/2014.
Analyzed pharmacy claims to develop predictive models of medication
adherence. Used \textbf{SAS and logistic
  regression} to analyze $\sim$ 300M claims from 61M individuals.
Designed and wrote all code (2,000 lines in
the final analysis). Pilot projects using multivariable adaptive
regression splines, and Fourier spectral analysis. Coursework in
\textbf{epidemiology, biostatistics, data mining, machine learning,
  and grant writing,} partially through Harvard School of Public
Health Program in Clinical Effectiveness. Professor: Kenneth Mandl.
Program director: Alexa McCray.

\textbf{Urgent care physician,} Harvard Vanguard Medical Associates,
10/15/2011\ndash{}6/30/2018. Diagnose and treat outpatients with acute
medical problems, e.g.\ infections, dehydration, sprains, abscesses,
lacerations, pelvic conditions, initial management of fractures.
Supervise nurse practitioners and physician assistants. Supervisor:
David Meenan.

\textbf{Internal medicine chief resident,} Saint Louis University
Hospital, 7/1/2010\ndash\linebreak[0]6/30/\linebreak[0]2011. Managed
and scheduled 130 residents. Academic appointment as instructor in
internal medicine. Attended on inpatient \& outpatient general
medicine in university and VA hospitals. Accepted transfers,
supervised and improved patient handoffs. Precepted medical students,
ran morbidity/mortality and clinicopathologic conferences, and $\sim
100$ resident report conferences. Interviewed and helped select
residency program applicants. Program director: Miguel Paniagua.

\textbf{Research elective,} 2/2007\ndash4/2007. Association rule
mining on a database of 12,000 outpatients and 40,000 diagnoses. Wrote
Perl code to find associations between any given pair of diseases in a
patient, and to output the strongest associations in an easily
visualized format. Professor: Walton Sumner, Washington University in
St.\ Louis.

\textbf{Professorial assistant,} 9/1998\ndash5/2002. Used molecular
biology and cell culture techniques to analyze factors leading to
malignant transformation of human cells. Professor: J.\ Justin
McCormick, Michigan State University.

\textbf{Technology skills.} Experience with \textbf{R} statistical
programming, \textbf{Git} source code management, and \textbf{SQL} all
since 2011; and with the \textbf{Python} programming language since
2013. Experience with \textbf{SAS} statistical programming 2011--2014.
GitHub username: zimolzak (have written code involving topics such as
a Twitter text generator, cryptography, satisfiability solving,
celestial navigation, and Amazon Web Services tasks). Experience with
the Perl programming language, Linux/UNIX, \LaTeX, and GNU Emacs since
2001. Intermediate experience with audio, video, and photo equipment
and editing. \emph{Electronic medical records:} experience with Epic
Hyperspace since 2009, CPRS/VistA since 2007, and 1 year experience
with Cerner PowerChart.

\textbf{Additional courses.} \emph{Machine Learning}
(Coursera/Stanford, Andrew Ng, Octave language, 2011). \emph{Intro to
Theoretical Computer Science} (Udacity, Sebastian Wernicke, Python
language, 2014). \emph{Tackling the Challenges of Big Data} (edX/MIT,
Daniela Rus, Sam Madden, Michael Stonebraker,
2/3/2015\ndash{}3/17/2015). \emph{Data Science Boot Camp} (Rice
University, in-person, Chris Jermaine, Devika Subramanian: numpy,
Jupyter, scikit-learn, 2019, 5 days). \emph{Machine Learning with
Python: From Linear Models to Deep Learning} (edX/MIT 6.86x, Regina
Barzilay, Tommi Jaakkola: \textbf{numpy and pytorch} for RNNs, CNNs,
etc., 2020, 11 weeks. Took 9600 words of notes with extensive
mathematical notation and wrote around 2000 lines of code. In-class
exercises average 95\%, projects average 100\%.)




\section*{Grants}

% Role: Title. Funder. Dates. Number. Amount. Description.

% consultant on IIR 22-071 – HSR Study (el serag, godwin)

Senior/key personnel: \textbf{Consortium for Translational and
  Precision Health.} NCATS. 09/01/2024\ndash{}07/31/2031. 1 UM1
TR004539-01A1. \$44.2 million. One of many senior/key personnel funded
on this large, multi-institution Clinical and Translational Science
Award.

Co-investigator: \textbf{Enhancing VA Implementation and Dissemination
  of Electronic Health Record Modernization through a National
  Collaborative Effort (EVIDENCE).} VA HSR\&D Service-directed
research. 10/2023\ndash{}9/2025.

Co-Investigator: \textbf{A Health Informatics Approach to Reduce
  Missed Opportunities for Barrett's Esophagus Screening.} American
College of Gastroenterology. 07/01/2023\ndash{}06/30/2026. Amount:
\$450,000.

Co-Investigator: \textbf{Houston Patient Safety Center of Inquiry:
  Diagnosis Improvement Safety Center (DISCovery).} VHA National
Center for Patient Safety. 10/01/2022\ndash{}09/30/2025. Amount:
\$1,185,000.

Co-Investigator: \textbf{Diagnostic Safety Center for Advancing
  E-triggers and Rapid Feedback Implementation (DISCOVERI).} AHRQ R18.
10/01/2022\ndash{}09/30/2026. 1 R18 HS029347-01. Amount: \$3,999,998.
Drafted a large portion of the proposal and managed multiple steps in
integrating sections, completing sections, and finalizing with
administrators.

Co-Investigator: \textbf{The Patient-Partnered Diagnostic Center of
  Excellence.} AHRQ R18. 10/01/2022\ndash{}09/30/2026. 1 R18
HS029356-01. \$4,000,000.

\subsection*{Completed}

Co-Investigator: \textbf{An Electronic Trigger Tool to Detect Missed
  Opportunities for Barrett’s Esophagus Screening.} Baylor College of
Medicine, Department of Medicine Physician-Scientist/Investigator
Faculty Development Award. 07/01/2022\ndash{}06/30/2024. Amount:
\$207,906.

Co-Investigator: \textbf{Measuring Missed Opportunities in the
  Diagnosis of Gastrointestinal Cancers.} Gordon and Betty Moore
Foundation. 7/1/2022\ndash{}12/31/2023. GBMF 11505. Amount: \$500,000
for 18 months.

Advisor: \textbf{Identifying current clinical care processes to
  reduce delays in colorectal cancer diagnoses.} Society to Improve
Diagnosis in Medicine, DxQI Seed Grant Program. Lead: Disha Kumar, VA
Chief Resident in Quality and Safety.

Co-Investigator: \textbf{Measuring and Improving the Safety of Test
  Result Follow-Up.} VA HSR\&D. 10/2018\ndash{}9/2023. I01 HX002439 /
IIR 17-127.

Co-PI: \textbf{Safer Dx e-measures to reduce preventable delays in
  cancer diagnosis.} Gordon and Betty Moore Foundation.
11/2019\ndash{}5/2021. GBMF 8838. Amount: \$520,162 for 18 months.
Drafted the majority of the proposal.

Co-Investigator: \textbf{Application of Machine Learning to Enhance
  e-Triggers to Detect and Learn from Diagnostic Safety Events.} AHRQ.
09/30/19\ndash{}09/29/2023. R01 HS027363-01. Amount: \$1,494,980.
% Til 2023 per Alexis email 2022-08-22
% 10% then 5%

Co-Investigator: \textbf{The Safer Dx Learning Lab: A Demonstration
  Project for Improving Diagnostic Safety.} Gordon and Betty Moore
Foundation. 6/30/2017\ndash{}5/31/2020. GBMF 5498. Amount: \$3,525,397
for 36 months.




\section*{Teaching}

\textbf{Student Scholarship and Inquiry Project}. 2023\ndash{}present.
Funded as faculty for a new curriculum component and course block,
designed to promote hypothesis-driven medical student scholarship on a
mentored project, with activities across all 4 years of medical
school. Serving as a liaison between information technology and
students, to construct an educational data warehouse extracted from
local electronic health records, for use in student projects.

\subsection*{Mentoring (long-term contact)}
% Reverse chronological. "Name (formality). Date. Description."

\textbf{Jennifer Sloane} (informal). 2022\ndash{}present. Postdoctoral
fellow in cognitive psychology. Mentored in clinical topics and VA
data environment.

\textbf{Theresa Nguyen} (formal). 9/2021\ndash{}present.
Fellow awarded Department of Medicine grant that includes me on
mentorship team. Mentoring in VA data availability and predictive
model application.

\textbf{Paarth Kapadia} (informal). 1/2020\ndash{}2023. MD student
at Baylor College of Medicine doing year-long research experience.
Mentored in manuscript preparation, data analysis, regulatory
compliance.

\textbf{Nathanael Fillmore} (formal). 2016\ndash{}2017.
Nonclinical PhD accepted to a VA advanced fellowship. As co-program
director for BD-STEP, I was responsible for training all fellows
regarding clinical topics, the data environment, and regulatory
compliance. Hired full-time by VA in 2017, informal mentoring
thereafter. Dr.\ Fillmore was later promoted to director of machine
learning at the Boston VA clinical trials center.

\textbf{Brett Johnson} (formal). 2016\ndash{}2017. BD-STEP
fellow. Responsibilities: see \emph{Fillmore} above. Hired full-time
by VA in 2017, informal mentoring thereafter.

\textbf{Justine Ryu} (formal \& informal). 7/2016 research elective,
through 2020 publication. Internal medicine resident at Boston
University. Mentored in exposure to machine learning techniques,
journal submission, and revision.

\textbf{Sahar Alkhairy} (informal). 2014\ndash{}2020. Undergraduate
and graduate student in computer science and molecular biology at MIT.
Mentored in research record keeping, clinical topics, journal
submission, and revision.




\subsection*{Mentoring (short-term contact)}

% fixme - eventually Jeanette Girard. Senior endo fellow. 2023+

\textbf{Adel Hassan} (informal). 2023\ndash{}present. Medical student
performing machine learning analyses. Mentored in clinical topics, VA
data environment, scientific publication, and regulatory compliance.

\textbf{Disha Kumar} (informal). 7/2022\ndash{}2023. Chief resident
in quality and safety at VA hospital. Mentored in data retrieval and
phenotyping strategies to identify inpatients with advanced cirrhosis,
and missed follow-up of colorectal cancer screening.

\textbf{Angela Wu} (informal). 2022. Computer science graduate student
performing machine learning and natural language processing analyses.
Mentored in clinical topics, VA data environment, and regulatory
compliance.

\textbf{Freddie Peng} (informal). 2021\ndash{}2022. Chief resident in
quality and safety. Mentored in data techniques to identify patients
with cirrhosis.

\textbf{Angela Rao} (informal). Chief resident in quality and safety.
Mentored in data techniques to measure usage of an inpatient diabetes
treatment order set.

\textbf{Max Yu} (informal). 12/2021\ndash{}2022. Computer science
undergraduate coming on board to assist in analysis. Mentored in
clinical topics, VA data environment, and regulatory compliance.




\section*{Credentials and Memberships}
\textbf{American Board of Internal Medicine} certified 8/10/2011,
participating in MOC.\\
\textbf{Clinical Informatics} board-certified 1/1/2014 (ABPM),
completed 2023 CCP, valid through 12/31/2029.\\
\textbf{Texas} full medical license 8/24/2018\ndash{}present. No.\ R8850,
exp 8/31/2026.\\
\textbf{Massachusetts} full medical license 7/20/2011\ndash{}present.
No.\ 249050 (inactive), exp 11/21/2025.\\
\textbf{Missouri} full medical license 6/25/2010\ndash{}present.
No.\ 2010020878, exp 1/31/2025\\
\textbf{American Medical Informatics Association} member
2011\ndash{}present.\\
\textbf{Early career physician council,} Massachusetts American
College of Physicians, 9/\linebreak[0]2011\ndash{}2015.\\
\textbf{USMLE}: passed Step 1 6/2005, Step 2 CS 4/2007, Step 2 CK
4/2007, Step 3 5/2010.\\
\textbf{ACLS and BLS} certified (exp 1/31/2026).




\section*{Honors and Awards}

% fixme Adel ML at med stud rsch day

\textbf{Most Creative Use of Tools,} Baylor College of Medicine
Datathon, April 2024. Project entitled ``An exploration of optimism in
medical record notes for pneumonia and associated patient length of
stay.''\\
\textbf{Best oral presentation of the conference,} Society to Improve
Diagnosis in Medicine, 10/2023. Title: ``Machine Learning for Enhanced
Electronic Trigger Detection of Diagnostic Errors.''\\
\textbf{GME Poster award,} MEDVAMC Education Day, 3/2023.
``Increasing Usage of an Inpatient Insulin Order Set.''\\
\textbf{Poster award,} BCM House Staff Research Symposium, 2023.
``Increasing Usage of an Inpatient Insulin Order Set.''\\
\textbf{Best of the best oral abstracts,} Society to Improve Diagnosis
in Medicine, 10/2022. Title: ``Implementation, validation, and
mortality association of 2 cancer diagnosis digital quality
measures.''\\
\textbf{Most innovative use of data,} Baylor College of Medicine
Datathon, April 2022. Project entitled ``The association of biased
language in medical text with diagnostic error.''\\
\textbf{Excellence in Collaboration,} Baylor College of Medicine
Datathon, October 2020. Project entitled ``Understanding predictors of
severe COVID-19 outcomes.'' One of the few projects to achieve
end-to-end success in identifying data elements, data extraction,
analysis, and results. All analyses performed by me in essentially 24
hours.\\
\textbf{Reviewers' Choice Abstract,} American Society of Human
Genetics Annual Meeting, 2017. Abstract entitled ``Developing
validated phenotypic cancer cohorts\ldots{}.''\\
\textbf{Finalist,} Surescripts 2014 Adherence Challenge. Member of a
team selected as one of ten finalists. Primary responsibility for
drafting the proposal. 8/15/2014\ndash{}1/8/2015.\\
\textbf{Third prize, patient safety \& quality improvement category,}
8/2010. American College of Physicians, Missouri Chapter Scientific
Meeting, associate poster competition.\\
\textbf{Tower Guard,} 1999\ndash{}2000. Service-oriented academic
honor society for Michigan State University sophomores.\\
\textbf{Distinguished Freshman Scholarship,} Michigan State
University. Competitive four-year full tuition scholarship awarded to
35 students out of the incoming class of about 10,000.




\section*{Publications}

% Format:
% Authors. (year) Title. Journal vol(iss):pages.

Zubkoff L, Zimolzak AJ, Meyer AND, \emph{et al.} \textbf{A Virtual
  Breakthrough Series Collaborative for Missed Test Results: A
  Stepped-Wedge Cluster-Randomized Clinical Trial.} JAMA Netw Open.
2024;7(10):e2440269. Published 2024 Oct 1.

Zimolzak AJ, Khan SP, Singh H, Davila JA. \textbf{Application of a
  digital quality measure for cancer diagnosis in Epic Cosmos.} J Am
Med Inform Assoc. Published online October 11, 2024.

Zimolzak AJ, Wei L, Mir U, \emph{et al.} \textbf{Machine Learning to
  Enhance Electronic Detection of Diagnostic Errors.} JAMA Netw Open.
2024;7(9):e2431982. Published 2024 Sep 3.

Kapadia P, Zimolzak AJ, Upadhyay DK, \emph{et al.} \textbf{Development
  and Implementation of a Digital Quality Measure of Emergency Cancer
  Diagnosis.} J Clin Oncol. 2024;42(21):2506--2515.

Honerlaw J, Ho YL, Fontin F, Gosian J, Maripuri M, Murray M, Sangar R,
Galloway A, Zimolzak AJ, Whitbourne SB, Casas JP, Ramoni RB, Gagnon
DR, Cai T, Liao KP, Gaziano JM, Muralidhar S, Cho K. \textbf{Framework
  of the Centralized Interactive Phenomics Resource (CIPHER) standard
  for electronic health data-based phenomics knowledgebase.} J Am Med
Inform Assoc. 2024;31(5):1126--1134.

Murphy DR, Zimolzak AJ, Upadhyay DK, Wei L, Jolly P, Offner A, Sittig
DF, Korukonda S, Rekha RM, Singh H. \textbf{Developing electronic
  clinical quality measures to assess the cancer diagnostic process.}
J Am Med Inform Assoc. 2023 Aug 18;30(9):1526\ndash{}1531.

Zimolzak AJ, Davila JA, Punugoti V, \emph{et al.} \textbf{Lessons
  learned from an enterprise-wide clinical datathon.} J Clin Transl
Sci. 2022;6(1):e125.

Meyer AND, Singh H, Zimolzak AJ, \emph{et al.} \textbf{Cancer
  Evaluations During the COVID-19 Pandemic: An Observational Study
  Using National Veterans Affairs Data.} Am J Prev Med.
2022;63(6):1026\ndash{}1030.

Zimolzak AJ, Singh H, Murphy DR, \emph{et al.} (2022)
\textbf{Translating electronic health record-based patient safety
  algorithms from research to clinical practice at multiple sites.}
BMJ Health Care Inform 29(1):e100565.

Zimolzak AJ, Shahid U, Giardina T, Memon S, Mushtaq U, Zubkoff L,
Murphy DR, Bradford A, Singh H. (2022) \textbf{Why Test Results Are
  Still Getting ``Lost'' to Follow-up: A Qualitative Study of
  Implementation Gaps.} Journal of General Internal Medicine
37(1):137\ndash{}144. Published online 2021-04-27.

\subsection*{Before 2022}

Alkhairy S, Celi LA, Feng M, Zimolzak AJ. (2021) \textbf{Acute Kidney
  Injury Detection Using Refined and Phys\-i\-o\-log\-i\-cal-Fea\-ture
  Augmented Urine Output.} Scientific Reports 11(1):19561.

Vassy JL, Gaziano JM, Green RC, Ferguson RE, Advani S, Miller SJ, Chun
S, Hage AK, Seo SJ, Majahalme N, MacMullen L, Zimolzak AJ, Brunette
CA. (2020) \textbf{Effect of Pharmacogenetic Testing for Statin
  Myopathy Risk vs Usual Care on Blood Cholesterol: A Randomized
  Clinical Trial.} JAMA Network Open 3(12):e2027092.

Ryu JH, Zimolzak AJ. (2020) \textbf{Natural Language Processing of
  Serum Protein Electrophoresis Reports in the Veterans Affairs Health
  Care System.} JCO Clinical Cancer Informatics 4:749\ndash{}756.

Brunette CA, Miller SJ, Majahalme N, Hau C, MacMullen L, Advani S,
Ludin SA, Zimolzak AJ, Vassy JL. (2020) \textbf{Pragmatic Trials in
  Genomic Medicine: The Integrating Pharmacogenetics in Clinical Care
  (I-PICC) Study.} Clinical and Translational Science
13(2):381\ndash{}390. Epub 2019-12-18.

Fillmore N, Do N, Brophy M, Zimolzak A. (2019) \textbf{Interactive
  Machine Learning for Laboratory Data Integration.} Stud Health
Technol Inform 264:133\ndash{}137.

Fillmore NR, Yellapragada SV, Ifeorah C, Mehta A, Cirstea D, White PS,
Rivero G, Zimolzak A, Pyarajan S, Do N, Brophy M, Munshi NC. (2019)
\textbf{With equal access, African Americans have superior survival
  compared to Caucasians with Multiple Myeloma: a VA study.} Blood
133(24):2615\ndash{}2618.

Vassy JL, Brunette CA, Majahalme N, Advani S, MacMullen L, Hau C,
Zimolzak AJ, Miller SJ. (2018) \textbf{The Integrating
  Pharmacogenetics in Clinical Care (I-PICC) Study: Protocol for a
  point-of-care randomized controlled trial of statin pharmacogenetics
  in primary care.} Contemp Clin Trials 75:40\ndash{}50.

Danziger J, Zimolzak AJ. \textbf{Residual Confounding Lurking in Big
  Data: A Source of Error.} In: MIT Critical Data, editors. Secondary
Analysis of Electronic Health Records. Cham, Switzerland: Springer;
2016. pp.\ 71\ndash{}78.

Fiore L, Ferguson RE, Brophy M, Kudesia V, Shannon C, Zimolzak A,
Pierce-Murray K, Turek S, Lavori P. (2016) \textbf{Implementation of a
  Precision Oncology Program as an Exemplar of a Learning Health Care
  System in the VA.} Fed Pract 33(suppl 1):S26\ndash{}S30.

Badawi O, Brennan T, Celi LA, Feng M, Ghassemi M, Ippolito A, Johnson
A, Mark RG, Mayaud L, Moody G, Moses C, Naumann T, Pimentel M, Pollard
TJ, Santos M, Stone DJ, Zimolzak A. (2014) \textbf{Making Big Data
  Useful for Health Care: A Summary of the Inaugural MIT Critical Data
  Conference.} JMIR Med Inform 2(2):e22.

Celi LA, Zimolzak AJ, Stone DJ. (2014) \textbf{Dynamic Clinical Data
  Mining: Search Engine-Based Decision Support.} JMIR Med Inform
2(1):e13.

Zimolzak AJ, Spettell CM, Fernandes J, Fusaro VA, Palmer NP, Saria S,
Kohane IS, Jonikas M, Mandl KD. (2013) \textbf{Early Detection of Poor
  Adherers to Statins: Applying Individualized Surveillance to Pay for
  Performance.} PLoS ONE 8(11):e79611.

Zimolzak AJ. \textbf{Medication Adherence: How Should We Measure It,
  and Can We Detect It Early?} Harvard Medical School, Master of
Medical Science thesis, 5/17/2013.




\section*{Presentations (national/international)} %reverse chron

% au, au. ti. conf. city, mm/dd/yyyy.

%% FIXME - gabe sandoval - va - regional

Zimolzak A, Zastrow R, Bezek S, Bradford A, Mir U, Ehsan S, Vaghani V,
Sittig D, Singh H. \textbf{Translating Electronic Trigger Tools to
  Partner Institutions for Learning and Exploration of Diagnostic
  Excellence.} DEX24. Minneapolis MN, 10/13/2024.

Kapadia P, Ali B, Zimolzak A, Singh H, Khalaf N. \textbf{Development
  of an Algorithm to Automate the Detection of Emergency Presentations
  Among Pancreatic Cancer Patients.} Digestive Disease Week.
Washington DC, 5/21/2024.

Zimolzak AJ, \emph{et al.} \textbf{Application of a Digital Quality
  Measure for Cancer Diagnosis in Epic Cosmos.} Oral and Poster
Presentation. Danish Society for Patient Safety Conference 2024. April
2024. Copenhagen, Denmark.

Zimolzak A, Kapadia P, Murphy DR, Upadhyay D, Mushtaq U, Mir U, Offner
A, Korukonda S, Murugaesh Rekha R, Abel G, Lyratzopoulos G, Mounce L,
Singh H. \textbf{Development, Implementation, and Validation of a
  Digital Quality Measure of Emergency Cancer Presentation.} Oncologic
Emergency Medicine Conference. Houston, 2/2024.

% sidm 2023

Zimolzak AJ, Yu M, Wu Y, Wei L, Mir U, Gupta A, Vaghani V, Hassan A,
Mower J, Subramanian D, Singh H. \textbf{Machine Learning for Enhanced
  Electronic Trigger Detection of Diagnostic Errors.} Society to
Improve Diagnosis in Medicine conference (awarded Best oral
presentation of the conference as a whole). Cleveland, 10/2023.

Zimolzak AJ, Singh H, Davila J. \textbf{Application of a Digital
  Quality Measure for Cancer Diagnosis in Epic Cosmos.} Society to
Improve Diagnosis in Medicine conference (oral presentation).
Cleveland, 10/2023.

Matin R, Meyer AND, Zimolzak AJ, Mir U, Giardina T, Singh H. \textbf{A
  Framework to Implement E-Triggers for Missed Opportunities in
  Diagnosis in Learning Health Systems.} Society to Improve Diagnosis
in Medicine conference. Cleveland, 10/2023.

% end sidm 2023

Kapadia P, Ali B, Zimolzak A, Singh H, Khalaf N. \textbf{Development
  of an Automated Algorithm to Detect Emergency Presentations Among
  Pancreatic Cancer Patients.} American College of Gastroenterology
annual meeting. Vancouver, 10/2023.

Carlson K, Kumar D, Comer L, Peng F, Rao A, Zimolzak A, Podany W,
Hirani K, Cole R, Vaclavik L, Horstman M, Larson S. \textbf{Increasing
  Accuracy of Colonoscopy Indication through Electronic Medical Record
  Changes: A Quality Improvement Project.} American College of
Gastroenterology annual meeting. Vancouver, 10/2023.

% end ACG

Kumar D, Carlson K, Peng FB, Rao A, Podany W, Hirani K, Zimolzak A,
Vaclavik L, Horstman M, Larson S. \textbf{Clinical Care Processes
  Causing Delay for Positive Colorectal Cancer Screening Diagnostic
  Colonoscopy Among Veterans.} Digestive Diseases Week. Chicago,
5/2023.

Sippel K, Zimolzak AJ, Davila JA, Punugoti V, Klotman PE, Petersen LA,
Liao G, Leiber L, Amos CI. \textbf{Datathon Revisited: Implementation
  of Lessons Learned.} Translational Science 2023. Washington DC,
4/2023.

Horstman MJ, Lim J, Zimolzak A, Caruso A, Gay L. \textbf{How we got
  our (S)WAG back: Academic Hospitalist (Strategic) Writing
  Accountability Group.} Society of Hospital Medicine National
Meeting. Austin, 3/2023.

Rao AN, Horstman M, Vaclavik L, Zimolzak A, Nguyen S, Sheth S,
Vasudevan M. \textbf{Increasing Usage of an Inpatient Insulin Order
  Set.} Michael E.\ DeBakey VA Medical Center Education Day, won award
in Graduate Medical Education category. Houston, 3/23/2023.

Zimolzak AJ, Zubkoff L, Shahid U, Giardina T, Memon S, Meyer AND,
Murphy DR, Singh H. \textbf{Reducing Missed Test Results through a
  Virtual Breakthrough Series Collaborative.} VA HSR\&D / QUERI
National Meeting. Baltimore; 2/9/2023.

% 2022

Zimolzak AJ, Kapadia P, Murphy DR, Upadhyay D, Mushtaq U, Mir U,
Offner A, Korukonda S, Murugaesh Rekha R, Abel G, Lyratzopoulos G,
Mounce L, Singh H. \textbf{Development/Implementation of Cancer
  Diagnosis Digital Quality Measures.} American Medical Informatics
Association Annual Symposium, selected for oral presentation.
Washington DC, 11/2022.

Peng FB, Kumar D, Vaclavik L, Horstman MJ, Zimolzak AJ, Jackson LK,
Braun UK, Hernaez R, Flores AG. \textbf{Quality improvement in
  palliative hepatology: increasing curative and palliative care for
  veterans with decompensated cirrhosis.} The Liver Meeting (AASLD,
poster). Washington DC, 11/2022.

Zimolzak AJ, Kapadia P, Murphy DR, Upadhyay D, Mushtaq U, Mir U,
Offner A, Korukonda S, Murugaesh Rekha R, Abel G, Lyratzopoulos G,
Mounce L, Singh H. \textbf{Implementation, validation, and mortality
  association of 2 cancer diagnosis digital quality measures.} Society
to Improve Diagnosis in Medicine conference (Best of the best oral
presentation). Minneapolis, 10/2022.

Zimolzak AJ, Choi D, Dawson D, Fletcher T, Scott T, Giardina T.
\textbf{The association of race and ethnicity with negative
  descriptors in clinical texts.} Society to Improve Diagnosis in
Medicine conference (oral presentation). Minneapolis, 10/2022.

% above here: SIDM, SIDM, AMIA, Liver Meeting

% begin amia cic

Zimolzak AJ, Singh H, Murphy DR, Wei L, Memon SA, Upadhyay D,
Korukonda S, Zubkoff L, Sittig DF. \textbf{Translating electronic
  health record-based patient safety research algorithms to multiple
  clinical sites.} American Medical Informatics Association Clinical
Informatics Conference, selected for oral presentation. Houston,
5/25/2022.

Murphy DR, Zimolzak AJ, Wei L, Jolly P, Offner A, Sittig DF, Singh H.
\textbf{Developing Digital Quality Measures to Assess Potential Missed
  Opportunities in Cancer Diagnosis.} American Medical Informatics
Association Clinical Informatics Conference. Houston, 5/25/2022.

Kapadia P, Zimolzak AJ, Murphy DR, Upadhyay D, Mushtaq U, Mir U,
Korukonda S, Murugaesh Rekha R, Wei L, Lyratzopoulos G, Abel G, Offner
A, Singh H. \textbf{A Digital Quality Measure of Emergency Cancer
  Diagnosis Using EHR Data in Two Large Health Systems.} American
Medical Informatics Association Clinical Informatics Conference,
selected for oral presentation. Houston, 5/25/2022.

% end amia cic

% begin datathon (amia, apha)

Zimolzak AJ, Davila JA, Punugoti V, Sippel KH, Balasubramanyam A,
Klotman P, Petersen LA, Rochat RH, Liao G, Laubscher RR, Leiber L,
Amos CI. \textbf{Lessons Learned from an Enterprise-Wide Clinical
  Datathon.} American Medical Informatics Association Annual
Symposium, selected for oral presentation. San Diego, 11/2/2021.

Zimolzak AJ, Davila JA, Amos CI. \textbf{Lessons learned from an
  enterprise-wide clinical datathon.} APHA 2021 Annual Meeting,
selected for oral presentation. Denver, 10/25/2021.

% end datathon
% begin sidm 2021

Zimolzak AJ, Murphy DR, Upadhyay D, Wei L, Mushtaq U, Jolly P,
Korukonda S, Lyratzopoulos G, Abel G, Offner A, Singh H.
\textbf{Development of an electronic quality measure of late stage
  cancer diagnosis.} Society to Improve Diagnosis in Medicine
conference (poster). 10/25/2021.

Meyer AND, Singh H, Zimolzak AJ, Wei L, Marinez A, Murphy DR.
\textbf{Association Between the COVID-19 Pandemic and Follow-up of
  Cancer-Related Abnormal Test Results.} Society to Improve Diagnosis
in Medicine conference. 10/2021.

Kapadia P, Zimolzak AJ, Murphy DR, Upadhyay D, Mushtaq U, Jolly P,
Korukonda S, Wei L, Lyratzopoulos G, Abel G, Offner A, Singh H.
\textbf{Development of an electronic diagnostic quality measure based
  on emergency cancer presentations in the United States.} Society to
Improve Diagnosis in Medicine conference, selected for oral
presentation. 10/2021.

% begin sidm 2020

Kapadia P, Zimolzak A, Murphy D, Lyratzopoulos G, Abel G, Upadhyay D,
Scott T, Singh H. \textbf{Development of eMeasures to Study Missed and
  Delayed Diagnosis of Lung and Colorectal Cancer.} Society to Improve
Diagnosis in Medicine conference. 10/19/2020.

Vaghani V, Murphy D, Memon S, Zimolzak A, Subramanian D, Upadhyay D,
Singh H. \textbf{A Portfolio of e-Triggers to Identify Diagnostic
  Errors in Emergency Departments: A Prioritization Exercise.} Society
to Improve Diagnosis in Medicine conference. 10/19/2020.

Kapadia P, Vaghani V, Zimolzak A, Singh H, Subramanian D.
\textbf{Development of a Machine Learning Enhanced Trigger to Detect
  Diagnostic Error.} Society to Improve Diagnosis in Medicine
conference. 10/20/2020.

Kapadia P, Murphy D, Zimolzak A, Lyratzopoulos G, Abel G, Scott T,
Singh H. \textbf{Measuring the Proportion of Cancer Diagnosed as an
  Emergency in the VA Health System.} Society to Improve Diagnosis in
Medicine conference. 10/20/2020.

% end sidm 2020

Vaghani V, Wei L, Mushtaq U, Zimolzak A, Sittig D, Singh H.
\textbf{Performance of an e-Trigger to Detect Missed Stroke Diagnosis
  in Patients with Headache or Dizziness Symptoms in Emergency
  Department.} American Medical Informatics Association Annual
Symposium. 11/16/2020.

% end amia 2020
% begin sidm 2019

Zimolzak A, Shahid U, Memon S, Giardina T, Mushtaq U, Murphy D,
Zubkoff L, Singh H. \textbf{Top Contributors to Missed Test Results in
  the VA Health Care System.} Diagnostic Error in Medicine 12th Annual
International Conference. Washington, D.C.; 11/11/2019.

Vaghani V, Wei L, Mushtaq U, Zimolzak A, Sittig D, Singh H.
\textbf{Performance of an e-Trigger to Detect Missed Stroke Diagnosis
  In Patients with Headache or Dizziness Symptoms in Emergency.}
Diagnostic Error in Medicine 12th Annual International Conference.
Washington, D.C.; 11/11/2019.

% end sidm 2019
% begin older boston presentations

Brunette CA, Advani S, Hage A, Seo S-J, Miller SJ, Majahalme N,
Zimolzak AJ, Vassy JL. \textbf{Impact of pharmacogenetic testing on
  statin outcomes: Primary results from the Integrating
  Pharmacogenetics in Clinical Care (I-PICC) Study randomized trial.}
American Society of Human Genetics Annual Meeting. Houston; October
19, 2019.

Do NV, Ramos JC, Fillmore NR, Grossman RL, Fitzsimons M, Elbers DC,
Meng F, Zimolzak AJ, Johnson BR, Ajjarapu S, DeDomenico CL,
Pierce-Murray KE, Hall RB, Do AF, Gaynor K, Elkin PL, Brophy MT.
\textbf{Machine learning methods to predict lung cancer survival using
  the Veterans Affairs Research Precision Oncology Data Commons.}
Medinfo (World Congress of Medical Informatics). Lyon, France;
8/26/2019.

Zimolzak A. \textbf{Early and late stage lung cancer: correlating
  clinical data and genomics in the Million Veteran Program.} American
Thoracic Society International Conference. Dallas; 5/20/2019.

Do N, Bono J, Fillmore N, Zimolzak A, Johnson B, Meng F, Elbers D,
Hall R, Ajjarapu S, Brophy M, Elkin P. \textbf{Development of an AI
  empowered Electronic Molecular Tumor Board Application Connected
  Utilizing the SMART on FHIR Framework.} American Medical Informatics
Association Annual Symposium. San Francisco; 11/5/2018.

Advani S, Brunette CA, Miller SJ, Majahalme N, MacMullen L, Hau C,
Zimolzak AJ, Vassy JL. \textbf{The Integrating Pharmacogenetics in
  Clinical Care (I-PICC) study: Baseline characteristics of
  participants in a point-of-care randomized trial.} American Society
of Human Genetics Annual Meeting. San Diego; 10/17/2018.

Johnson BR, Elbers DC, Pierce E, Meng F, Fillmore N, Ayandeh S, Chen
D, Selva L, Begley NB, Zimolzak AJ, Brophy MT, Do NV. \textbf{The
  Veterans Health Administration's Research Precision Oncology
  Project: Integrating Real-World Data into a Learning Health System.}
American Society of Human Genetics Annual Meeting. San Diego;
10/18/2018.

Brunette CA, Miller SJ, Majahalme N, Hau C, MacMullen L, Advani S,
Zimolzak AJ, Vassy JL. \textbf{Pragmatism in Pharmacogenetics Trials:
  A PRECIS-2 perspective on the Integrating Pharmacogenetics in
  Clinical Care (I-PICC) Study.} American Society of Human Genetics
Annual Meeting. San Diego; 10/19/2018.

Do N, Pierce-Murray K, Peirce E, DeDomenico C, Meng F, Elbers D,
Katcher B, Hall R, Zimolzak A, Ajjarapu S, Shannon C, Turek S, Johnson
B, Fillmore N, Brophy M, Fiore L. \textbf{The Development of the
  Research Precision Oncology Program Data Repository (PODR) in the
  Veterans Affairs Healthcare System.} American Medical Informatics
Association Annual Symposium. Washington, D.C.; 11/6/2017.

Ajjarapu S, Meng F, Elbers D, Do N, Hall R, Pierce-Murray K, Selva L,
Katcher B, Johnson B, Zimolzak A, DeDomenico C, Brophy M, Fiore L.
\textbf{Releasing De-identified Clinical, Imaging, and Genomic Data
  from the VA to External Repositories for the APOLLO Network.}
American Medical Informatics Association Annual Symposium. Washington,
D.C.; 11/6/2017.

Majahalme N, Miller S, Zimolzak A, Vassy J. \textbf{Scaling Down
  Clinical Trial Software from 13,500 to 400 Participants.} American
Medical Informatics Association Annual Symposium. Washington, D.C.;
11/6/2017.

Miller SJ, Hau C, Majahalme N, Zimolzak AJ, MacMullen L, Vassy JL.
\textbf{Potential impact of statin pharmacogenetic testing in an
  integrated healthcare system: The Integrating Pharmacogenetics in
  Clinical Care (I-PICC) Study.} American Society of Human Genetics
Annual Meeting. Orlando; 10/19/2017.

Johnson BR, Fillmore N, Zimolzak A, Ho YL, Elbers D, Katcher B, Gagnon
D, Meng F, Brophy M, Fiore L, Lesse A, Concato J, Gaziano JM, Do N,
Elkin PL, Cho K. \textbf{Developing validated phenotypic cancer
  cohorts for molecular stratification and susceptibility assessment,
  a use case: patients diagnosed with early versus late stage
  non-small cell lung cancer.} American Society of Human Genetics
Annual Meeting. Orlando; 10/19/2017.

Zimolzak AJ, Kudesia VM. \textbf{Secondary Use of an
  Eighty-Billion-Row Clinical Data Warehouse.} Society for Industrial
and Applied Mathematics 2016 annual meeting. Boston; 7/14/2016.

Raju SP, Ho Y-L, Zimolzak AJ, Katcher B, Cho K, Gagnon DR.
\textbf{Validation of Laboratory Values in a Heterogeneous Healthcare
  System: The US Veterans Affairs Experience.} 31st International
Conference on Pharmacoepidemiology \& Therapeutic Risk Management
(ICPE). Boston; 8/22\ndash{}26/2015.

Leatherman SM, Riley KE, Woods PA, Zimolzak AJ, Majahalme N, Kudesia
V, Ferguson RE, Fiore LD. \textbf{Ascertainment of Clinical Outcomes
  from Electronic Medical Record Data for Point-of-Care Clinical
  Trials.} VA HSR\&D / QUERI National Conference. Philadelphia;
7/\linebreak[0]8\ndash{}\linebreak[0]10/\linebreak[0]2015.

Zimolzak AJ. \textbf{Early Detection of Statin
  Adherence/Nonadherence.} National Library of Medicine Informatics
Training Conference, Salt Lake City; 6/19/2013.

Zimolzak AJ, Spettell CM, Fernandes J, Fusaro VA, Palmer NP, Saria S,
Jonikas M, Kohane IS, Mandl KD. \textbf{Early Statin Adherence As a
  Predictor of Later Adherence.} American Medical Informatics
Association Summit on Clinical Research Informatics. San Francisco;
3/20/2013.




\section*{Presentations (local seminars, course lectures)}
%reverse chron

% fixme - the 3 datathons?

Zimolzak AJ. \textbf{Electronic Health Record Data Quality.} Lecture.
7/2024. https://zenodo.org/doi/10.5281/zenodo.11393188

Zimolzak AJ. \textbf{Electronic Health Record Data for Health Policy
  Research.} Invited lecture to medical students in the health policy
track. 12/5/2023. https://doi.org/10.5281/zenodo.10267057

Zimolzak AJ. \textbf{Clinical Research Informatics with Applications
  to Diagnostic Safety.} Invited presentation to Patient-Partnered
Diagnostic Center of Excellence learning community. 8/21/2023.

Zimolzak AJ. \textbf{Is it called Artificial Intelligence, or Machine
  Learning, or something else?} Invited presentation to IQuESt
methodology core. 5/26/2023.

Zimolzak AJ. \textbf{Working with data sets for translational
  research.} Baylor College of Medicine course ``Orientation to
Clinical Translational Research,'' course no.\ GS-GS-6206. Second-year
PhD students in the Graduate School of Biomedical Sciences. 2023.

Zimolzak AJ. \textbf{Working with data sets for translational
  research.} Baylor College of Medicine course ``Orientation to
Clinical Translational Research,'' course no.\ GS-GS-6206. Second-year
PhD students in the Graduate School of Biomedical Sciences. 8/16/2022.

Zimolzak AJ. \textbf{Concept embeddings for stroke diagnostic error.}
Gulf Coast Consortia Artificial Intelligence in Healthcare Symposium.
5/18/2022.

Zimolzak AJ. \textbf{Translating Electronic Health Record-Based
  Patient Safety Algorithms from Research to Clinical Practice.}
Invited seminar talk, Baylor College of Medicine, Computational and
Integrative Biomedical Research Center. Quantitative \& Computational
Biosciences graduate seminar. 2/23/2022.

Zimolzak AJ. \textbf{Data processes and machine learning for health
  research, in the US Department of Veterans Affairs.} Invited seminar
talk, University of Houston Department of Industrial Engineering.
4/16/2021.

Johnson BR, Fillmore NR, Brophy M, Fiore LD, Elkin PL, Katcher B, Ho
Y-L, Zimolzak AJ. \textbf{Phenotyping Non-Small-Cell Lung Cancer at
  the VA: Cohort and Susceptibility Analysis.} VA Research week.
Boston; 5/18/2017.

Fillmore NR, Zimolzak AJ, Johnson BR, Brophy M, Munshi N.
\textbf{Ascertaining Cases of Multiple Myeloma Using Multiple VA
  National Structured Data Sources.} VA Research week. Boston;
5/18/2017.




\section*{Professional Service}

\textbf{Phenotype Working Group,} part of BCM Department of Medicine
Learning Health System initiative. 2023\ndash{}present.\\
\textbf{Artificial intelligence Request for applications,} reviewer.
BCM-wide funding opportunity for AI projects. 2024.\\
\textbf{BCM Data Governance Committee,} member. 2024\ndash{}present.\\
\textbf{Internal grant review,} IQuESt. 2023\ndash{}present. Critiqued
faculty and career development grants (3).\\
\textbf{Faculty candidate interviewer,} IQuESt. 2023\ndash{}present.\\
\textbf{VA CIPHER expert panel,} 2024. Advise on the future direction
of the Centralized Interactive Phenomics Resource.\\
\textbf{Electronic laboratory notebook working group,} Baylor College
of Medicine. 10/2021\ndash{}7/2022.\\
\textbf{Research Data Security Committee,} IQuESt.
2/2022\ndash{}present.\\
\textbf{House Staff Research Symposium,} reviewer. BCM department of
medicine. 4/2022.\\
\textbf{Lung Precision Oncology Project,} grant review section. VA
Central Office  (CSR\&D). 9/2020.\\
\textbf{Methods Analytics and Data Education Initiative,} IQuESt.
1/2020\ndash{}present.\\
\textbf{Patient, Physician, and Society} preceptor, Baylor College of
Medicine 2019\ndash{}20.\\
\textbf{Institutional Review Board,} member, VA Boston Healthcare System.
9/2017\ndash{}11/2018.\\
\textbf{NEJM Group Open Forum.} Moderator for a forum where
authors discuss their NEJM articles. 2/2015\ndash{}3/2015.\\
\textbf{F1000Research,} reviewer. 3/2021\ndash{}present. See also
https://f1000research.com/articles/9-1186\\
\textbf{JCO Clinical Cancer Informatics,} reviewer. 2/2020\ndash{}present.\\
\textbf{Digital Health,} reviewer. 12/2019\ndash{}present.\\
\textbf{JMIR Research Protocols,} reviewer. 1/2019\ndash{}present.\\
\textbf{PLoS ONE,} reviewer. 11/2012\ndash{}present.\\
\textbf{Journal of Health Services Research \& Policy,} reviewer.
8/2015\ndash{}present.\\
\textbf{Diagnosis,} ad-hoc reviewer. 2024\ndash{}present.\\
\textbf{AMIA Annual Symposium,} reviewer. 2015\ndash{}present.\\
\textbf{Physicians and Social Media: Keeping it Professional.}
Planning committee member, panel moderator. 9/26/2013.\\
\textbf{Critical Data.} Planning committee, participant. ``Data
marathons'' at MIT. 1/3/2014\ndash\linebreak[0]1/7/2014, and
9/5/2014\ndash{}9/7/2014.\\
\textbf{Computing in Cardiology.} Planning committee \& reviewer.
Three day conference for international participants from medicine,
physics, engineering and computer science.
9/8/2014\ndash{}9/10/2014.\\
\textbf{Massachusetts American College of Physicians Annual Scientific
  Meeting.} Planning committee, quiz moderator, reviewer.
2014\ndash{}2016.




\section*{References}
\begin{tabular}{llll}

Hardeep Singh & 2002 Holcombe Blvd              & Houston TX 77030 & x-singh\\
Chris Amos    & One Baylor Plaza                & Houston TX 77030 & x-amos\\
Andrew Caruso & 2002 Holcombe Blvd Mailcode 111 & Houston TX 77030 & x-caruso\\
Lindsey Gay   & 2002 Holcombe Blvd Mailcode 111 & Houston TX 77030 & x-gay\\
\hline
Mary Brophy & 150 S.\ Huntington, mail stop 151MAV & Boston MA 02130 & x-brophy\\
Nhan Do     & 150 S.\ Huntington, mail stop 151MAV & Boston MA 02130 & x-do\\

Jay Orlander    & 1400 VFW Pkw      & West Roxbury MA 02132 & x-wrox\\
Anthony Breu    & 1400 VFW Pkw      & West Roxbury MA 02132 & x-wrox\\
Valmeek Kudesia & 30 Winter St      & Boston MA 02108       & x-kudesia\\
Kenneth Mandl   & 300 Longwood Ave  & Boston MA 02115       & x-mandl\\
David Meenan    & 133 Brookline Ave & Boston MA 02215       & x-meenan\\
Alexa McCray    & 10 Shattuck St    & Boston MA 02115       & x-mccray\\
Miguel Paniagua & 3750 Market St    & Philadelphia PA 19104 & x-paniagua
\end{tabular}

\end{document}

% LocalWords:  ocity hcity bday bplace PGY Desloge Shattuck MAVERIC
% LocalWords:  BD Nhan Valmeek Kudesia Brophy Fiore Orlander Breu ra
% LocalWords:  Celi ry SAS Mandl Alexa Meenan handoffs Precepted edX
% LocalWords:  clinicopathologic Paniagua zimolzak PowerChart Udacity
% LocalWords:  Coursera Daniela Rus Stonebraker Devika Subramanian Yu
% LocalWords:  Barzilay Tommi Jaakkola pytorch RNNs CNNs DISCovery AJ
% LocalWords:  GBMF Kapadia Nathanael Ryu Alkhairy MOC phenotypic DT
% LocalWords:  Surescripts Choi Marinez Fea ture Shahid Giardina JL
% LocalWords:  Mushtaq Vassy Gaziano JM Advani Chun Hage Seo Statin
% LocalWords:  Majahalme MacMullen Pharmacogenetic Myopathy JH JCO SV
% LocalWords:  Hau Ludin Pharmacogenetics Epub Technol Yellapragada
% LocalWords:  Ifeorah Mehta Cirstea Rivero Pyarajan Munshi Contemp
% LocalWords:  Clin Danziger Cham Springer Turek Lavori Pract Badawi
% LocalWords:  Ghassemi Ippolito RG Mayaud Naumann Pimentel TJ JMIR
% LocalWords:  Spettell Fernandes Fusaro Saria Kohane Jonikas KD PLoS
% LocalWords:  Adherers Statins Upadhyay Offner Korukonda Murugaesh
% LocalWords:  Rekha Lyratzopoulos Mounce Peng FB Kumar Vaclavik MJ
% LocalWords:  Horstman LK Hernaez AASLD DF Biosciences JA Punugoti
% LocalWords:  Sippel KH Balasubramanyam Klotman Rochat Liao Leiber
% LocalWords:  Laubscher APHA eMeasures Vaghani JC Grossman RL Elbers
% LocalWords:  Fitzsimons Meng Ajjarapu DeDomenico KE Gaynor Elkin De
% LocalWords:  Medinfo Ayandeh Selva Begley Peirce Katcher PODR YL LD
% LocalWords:  Gagnon Lesse Concato Cho VM Raju Pharmacoepidemiology
% LocalWords:  ICPE Leatherman Nonadherence llll singh amos Mailcode
% LocalWords:  caruso MAV brophy Pkw wrox kudesia Longwood mandl DxQI
% LocalWords:  meenan mccray paniagua DISCOVERI Disha Gosian Maripuri
% LocalWords:  Sangar Whitbourne Casas Ramoni Cai Muralidhar ocad
% LocalWords:  Prev Podany Hirani Sheth Vasudevan
